%-------------------------
% CV for Northeastern University Faculty in Latex
% Author : Zoe Kearney
% Based off of: https://www.overleaf.com/latex/templates/coles-resume-template/qhpynjcvjpcj
% Follows: https://theprofessorisin.com/2016/08/19/dr-karens-rules-of-the-academic-cv/
% License : MIT
%------------------------

% Document class and font size
\documentclass[a4paper,9pt]{extarticle}

% Packages
\usepackage[utf8]{inputenc} % For input encoding
\usepackage{geometry} % For page margins
\geometry{a4paper, margin=1in} % Set paper size and margins
\usepackage{titlesec} % For section title formatting
\usepackage{enumitem} % For itemized list formatting
\usepackage{hyperref} % For hyperlinks

% Formatting
\setlist{noitemsep} % Removes item separation
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule] % Section title format
\titlespacing*{\section}{0pt}{\baselineskip}{\baselineskip} % Section title spacing

% Begin document
\begin{document}

% Disable page numbers
\pagestyle{empty}

% Header
\begin{center}
\textbf{\Large Micah Banschick }\\[3pt] % Name
\textbf{Curriculum Vitae}\\[1pt] % CV
Stamford, CT | \href{mailto:micah.banschick@uconn.edu}{micah.banschick@uconn.edu} | (914) 714-3677 | \href{https://www.linkedin.com/in/micah-banschick/}{linkedin.com/in/micah-banschick/} | Country Citizen % Contact info
\end{center}

%------------------------

% Education Section
\section*{EDUCATION}

\noindent
\newline
\textbf{B.Sc. in Physics and Mathematics} \\
Year of completion: 2027 \\ 
University of Connecticut \\ 
\textit{Thesis}: [Project Title] - \textit{Advisor}: Professor Peter Schweitzer \\
GPA: 3.70 \\

%------------------------

% Employment Section
\section*{EMPLOYMENT}
\noindent
\newline
\textbf{Java API Engineer} \\
Year-Year: XXXX-2023 \\
Synchrony Financial \\ 
(Encoded and debugged files from the team assigned to API preferences and notifications for the Monster corporation according to the team’s Jira storyboard in bi-weekly sprints.) \\ 

\noindent
\textbf{Software Engineer} \\
Year-Year: 2021-Present \\
CyberPR Army \\ 
(Designs website structure and style for various pages through an extensive knowledge of CSS.) \\

\noindent
\textbf{AFRL Scholar} \\
Year-Year: XXXX-2024 \\
Air Force Research Laboratory \\ 
(Researched Optical Signatures of Ion-neutral Collisions on-site.) 

%------------------------

% Research Experience Section 
\section*{RESEARCH EXPERIENCE}

\noindent
\newline
\textbf{Merging Supermassive Black Hole Binary Systems} - \textit{Advisor: Prof. Jonathan Trump} \\
Year - Year: 2024 - Present \\
University of Connecticut\\
Calculated the spectral emission distributions of supermassive black holes by integrating radially through their
mini-disks. \\

\noindent
\textbf{Quantum Computation Power with Qubit} - \textit{Advisor: Prof. Lea Ferreira dos Santos} \\
Year - Year: 2024 - Present \\
University of Connecticut\\
Analyzed the matrix symmetry of the Kerr Hamiltonian representing the observables of a qubit. \\

\noindent
\textbf{Optical Signatures of Ion-neutral Collisions} - \textit{Advisor: Dr. Benjamin Prince} \\
Year - Year: XXXX - 2024 \\
Air Force Research Laboratory\\
Maecenas ultricies augue a turpis viverra iaculis. Fusce a lorem est. \\

\noindent
\textbf{Predicting Stock Trends Using LSTM-Neural Networks} - \textit{Advisor: Prof. Phillip Bradford} \\
Year - Year: 2021 - XXXX \\
University of Connecticut\\
Used TensorFlow and LSTM-Neural Networks to predict Stock trends and collaborated weekly with the research supervisor about how to improve the program. \\

\noindent
\textbf{Psychology of Human Expression} - \textit{Advisor: Yuvalal Liron} \\
Year - Year: 2016 - 2017 \\
Weizmann Institute of Science\\
Simulated over 500 instances of expression through mock-illustrations and recorded results.

%------------------------

% Conference Activity Section 
\section*{CONFERENCE ACTIVITY}

\subsection*{Posters Presented}
\textbf{Luminescence Measurements of Charge Transfer Collisions of $N^+_2 + N_2$} \\
Date: 2024 \\
Air Force Research Laboratory Poster Session \\
Nam suscipit et nisi a aliquet. Fusce metus lacus, porta a viverra et, tristique pharetra magna. Cras in leo sem. Etiam ut vehicula massa, eu semper est. Integer quis eros sapien. Quisque sed pellentesque metus. Sed a augue quis mi dictum pharetra.

%------------------------

% Awards and Honors Section
\section*{AWARDS AND HONORS}

\noindent
\textbf{Philips Scholar},\ USRA,\ \$11,838.40 \hfill 2024

\noindent
\textbf{Honors Scholar in Physics},\ University of Connecticut \hfill 2023 - 2027

\noindent
\textbf{Annual Physics Award},\ University of Connecticut \hfill 2023 

\noindent
\textbf{Annual Mathematics Award},\ University of Connecticut \hfill 2023

\noindent
\textbf{Dean's List},\ University of Connecticut \hfill 2023

%------------------------

% Teaching Experience Section
\section*{TEACHING EXPERIENCE}

\noindent
\textbf{Electricity Lessons Using Vandergraff Generator},\ Hartford Public High School \hfill 2024

\noindent
\textbf{Gravity Lessons Through Projectile Motion},\ Hartford Public High School \hfill 2024

%------------------------

% Professional Memberships Section 
\section*{PROFESSIONAL MEMBERSHIPS}

\noindent
\newline
\textbf{Society of Physics Students},\ University of Connecticut \hfill 2023

\noindent
\textbf{Science Technology and Astronomy Recruits},\ University of Connecticut \hfill 2023

\noindent
\textbf{Phi Sigma Pi},\ University of Connecticut \hfill 2023

%------------------------

% References Section 
\section*{REFERENCES}

\noindent
\newline
\textbf{Jonathan Trump} \\
\textit{Associate Professor} \\
Dept. of Physics, University of Connecticut \\
196A Auditorium Road, Unit 3046 \\
Storrs, CT 06269-3046\\
jonathan.trump@uconn.edu \\
(860)486-6310 \\

\noindent
\textbf{Lea Ferreira dos Santos} \\
\textit{Associate Department Head for Administration and Professor} \\
Dept. of Physics, University of Connecticut \\
196A Auditorium Road, Unit 3046 \\
Storrs, CT 06269-3046\\
lea.santos@uconn.edu \\
(860) 486-6748 \\

\noindent
\textbf{Peter Schweitzer} \\
\textit{Associate Department Head for Undergraduate Affairs and Professor} \\
Dept. of Physics, University of Connecticut \\
196A Auditorium Road, Unit 3046 \\
Storrs, CT 06269-3046\\
peter.schweitzer@uconn.edu \\
(860) 486-0443 \\


% End document
\end{document}
