\documentclass[11pt]{article}
\usepackage{graphicx} % Required for inserting images
\setlength{\parindent}{0pt}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc}
\usepackage[brazil]{babel}
\usepackage{lipsum}
\usepackage[left=1.06cm,top=1.7cm,right=1.06cm,bottom=0.49cm]{geometry}




%by: Aline R. Antunes

\begin{document}
\begin{center}
    \textbf{Micah Banschick}\\ 
    \hrulefill
\end{center}

\begin{center}
    Stamford, CT 06905 \textbullet \ \href{mailto:micah.banschick@uconn.edu}{micah.banschick@uconn.edu} \textbullet \ (914) 714-3677 \textbullet \ \href{https://www.linkedin.com/in/micah-banschick/}{linkedin.com/in/micah-banschick/}
\end{center}

\vspace{0.5pt}

\begin{center}
    Engineer with a background working effectively in research labs and environments. Experienced in the Python, Matlab, and Latex programming languages to record, analyze, and model results effectively. Possess strong skills in team-building and project management that help businesses develop quality products and drive up profits. Focused on achieving project objectives with reliability and precision.
\end{center}

\begin{center}
    \textbf{Experience}
\end{center}
\textbf{Air Force Research Laboratory} - \textit{Secret Level Security Clearance} \hfill Kirtland Air Force Base, NM

\textbf{AFRL Scholar} \hfill May 2024 – August 2024
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Experimentally gathered optical emissions of $N^+_2 + N_2$ collisions for $N^+_2(B-X)$ and $N^+_2(A-X)$ between $16\ \frac{eV}{q}$ and $600\ \frac{eV}{q}$ kinetic energies using a $13.86\ MHz$ radio frequency ion source.
    \item Analyzed vibrational and rotational transitions through the generation of basis functions calculated in Diatomic, with subsequent simulation of the data accomplished with IgorPro.
\end{itemize}

\vspace{12pt}

\textbf{Synchrony Financial} \hfill Stamford, CT

\textbf{Java API Engineer} \hfill May 2023 – November 2023
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Encoded and debugged files from the team assigned to API preferences and notifications for the Monster corporation.
    \item Contributed to completing all assignments on the team’s Jira storyboard according to bi-weekly sprints.
    \item Organized weekly community events for the Stamford DTC interns.
\end{itemize}

\vspace{12pt}

\textbf{CyberPR Army} \hfill Remote

\textbf{Software Engineer} \hfill May 2021 – Present
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Designs website structure and style for various pages through an extensive knowledge of CSS.
    \item Updates information with new data on old website pages with WordPress tools.
    \item Explores avenues and examples across the internet to best approach and design new projects.
\end{itemize}

\vspace{12pt}

\begin{center}
    \textbf{Education}
\end{center}
\textbf{University of Connecticut} \hfill Storrs, CT

B .Sc. in Physics and Mathematics (Honors). \hfill Graduation Date: May 2027

Thesis: [To be determined] - \textit{Advisor: Prof. Peter Schweitzer}

\vspace{12pt}

\begin{center}
    \textbf{Leadership \& Activities}
\end{center}

\textbf{Meetup}	\hfill Stamford, CT

\textbf{Organizer} \hfill Sep 2021 – Present
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Created 3 social groups through the Meetup app for Board Games, Anime/Manga, and D\&D.
    \item Gathered $\sim 500$ members across the 3 groups during the Covid-19 pandemic.
    \item Leads weekly events for people to meet each other and create a community.
\end{itemize}

\begin{center}
    \textbf{Skills \& Interests}
\end{center}

\textbf{Engineering:} Aerospace, Electrical, Mechanical, Software, Financial

\textbf{Technical:} Python, Mathematica, Matlab, LaTeX, Javascript, Java, Ruby, React, Redux, AI, Cryptotechnology

\textbf{Interests:} Guitar, Piano, Choir, Theater, Dungeons and Dragons, Board Games, Anime/Manga




\end{document}
